Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-14 Paper_presentation.tex
Sections added
More content...

\begin{block}{Bloco}

%começa um novo bloco (caixa no slide)

O que eu escrever aqui aparece no bloco.

\end{block} %finaliza o bloco

\begin{block}{Outro bloco}

Posso criar vários blocos em um \textit{frame}...
E fazer com que apareçam um de cada vez...

\end{block} \pause %o comando "\pause" insere uma pausa no slide

\begin{block}{Bloco oculto}

Este bloco só vai aparecer quando eu "clicar" ou pressionar uma tecla.

@@

\section{Criminal Investigation}
\begin{frame}{Slide com \textit{bullets}}

\begin{itemize} 
    \item[\checkmark] Works properly and is evaluated under the goal of the investigations.
    \item[\checkmark] We follow that principles, (basic principles) rather than isolated characterization of the users.
    \item[\checkmark] We wil review the USA\footnote{Fourth Amendment and related jurisprudence} Law under the constraints of criminal investigations for Children Pornograph.
\end{itemize}

>>>>

\section{Criminal Investigation}
\begin{frame}

\begin{itemize} 
    \item[\checkmark] Works properly and is evaluated under the goal of the investigations.

    \item[\checkmark] We follow that principles, (basic principles) rather than isolated characterization of the users.

    \item[\checkmark] We will review the USA\footnote{Fourth Amendment and related jurisprudence} Law under the constraints of criminal investigations for Children Pornograph.
\end{itemize}

\begin{frame}
\begin{block}{Works properly and is evaluated under the goal of the investigations}

\begin{itemize}

\item[\checkmark]That  means: The criminal investigation is increasingly advanced and with more development tools for this one.

\item[\checkmark]There are always more groups that works to find and to discover and try to prevent Child Pornography (CP).

\item[\checkmark]But it is very difficult do prevent, because of the large scale growth in the worldwide web. There are over 1,8 milion CP in internet ''found on eMule'' (we estimate much more).

\end{itemize}

@@

\begin{frame}
\begin{block}{Basic principles rather than isolated characterization of the users}

\begin{itemize}

\item[\checkmark]This means that we will not discuss about a particular user, but the market situation that involves this type of crime.

\item[\checkmark]In criminal investigations of the type we consider search warrants must specify this location, and not a person (not a user).

\item[\checkmark]Actions by the investigators are shortened by law ''Fourth Amendment and Related Jurisprudence'', where this means that the user has a protection on a electronic data.

\end{itemize}

\begin{frame}
\begin{block}{What is wrong with Fourth Amendment Jurisprudence?}

\textbf{The Third Party Doctrine}

According to the Supreme Court's third party doctrine, personal information, once exposed to any third party, loses all Fourth Amendment protection. Some information exposed to third parties is protected by various statutes, but those can be inconsistent and outdated. The Electronic Communications Privacy Act (ECPA), for example, is notably out of date, leaving privacy protection of technology, as the Ninth Circuit put it, ''a confusing and uncertain area of the law.''. Some privacy interests that are currently unprotected under the Fourth Amendment. Konop ... also receive protection under the First Amendment – but that protection is far from comprehensive... (1967)

\section{Forensic Measurement}
\begin{frame}

\section{Availability and Resilience}
\begin{frame}

\section{FOI Redundancy and Availability}
\begin{frame}

\section{Comparing Aggressive Peers}
\begin{frame}

\section{Analysis of User Aliasing}
\begin{frame}

\section{Measurement Limitations}
\begin{frame}

\section{Related Work}
\begin{frame}

\section{Conclusions and Future Work}
\begin{frame}
